### 2015-03-11 fundamentals/examples.tex
adds label to simulation section}
fixes links and stuff in bib.

Early progress has been promising. Many archetypes external to the \Cycamore
library (Table \ref{tab:cycamore}) have been
\cite{huff_streamblender_2014,huff_commodconverter_2014} or are being
\cite{flanagan_bright-lite_2014,skutnik_nuclear_2014,huff_mktdriveninst_2014}
developed for contribution to the \Cyclus ecosystem. These archetypes provide
the first examples of developer-contributed capabilities.  They add to the
fundamental \Cycamore archetypes by providing physics-based reactors,
separations logic, fuel fabrication processing, storage facilities, and expanded
institutional paradigms.  The existence and diversity of these contributed
archetypes illustrate the power and potential of the community-based development
approach that \Cyclus has taken.

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Bright-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{flanagan_bright-lite_2014} \\
Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{skutnik_nuclear_2014} \\
CommodConverter & A simple commodity converting storage facility archetype  & \cite{huff_commodconverter_2014} \\
MktDrivenInst & An institution that controls deployment based on commodity availability & \cite{huff_mktdriveninst_2014} \\
SeparationsMatrix & A facility for elemental separations of used fuel & \cite{huff_streamblender_2014} \\
StreamBlender & A facility for fuel fabrication from reprocessed streams & \cite{huff_streamblender_2014} \\
\hline
\end{tabularx}
\caption{A diverse set of archetypes under development reflect the diverse
needs of researchers at various institutions. These archetypes, contributed
outside of the \Cyclus core and \Cycamore libraries are the first demonstration
of community-driven development in a fuel cycle simulator.}
\label{tab:archetypes}
\end{table}

\subsection{Simulations}
%Inpro example (is this still running or did we deprecate it with 1.0?)

>>>>

Early progress has been promising. Many archetypes external to the \Cycamore
library (Table \ref{tab:cycamore}) have been
\cite{huff_streamblender_2014,huff_commodconverter_2014} or are being
\cite{flanagan_bright-lite_2014,skutnik_development_2015,huff_mktdriveninst_2014}
developed for contribution to the \Cyclus ecosystem. These archetypes provide
the first examples of developer-contributed capabilities.  They add to the
fundamental \Cycamore archetypes by providing physics-based reactors,
separations logic, fuel fabrication processing, storage facilities, and expanded
institutional paradigms.  The existence and diversity of these contributed
archetypes illustrate the power and potential of the community-based development
approach that \Cyclus has taken.

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Bright-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{flanagan_bright-lite_2014} \\
Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{skutnik_development_2015} \\
CommodConverter & A simple commodity converting storage facility archetype  & \cite{huff_commodconverter_2014} \\
MktDrivenInst & An institution that controls deployment based on commodity availability & \cite{huff_mktdriveninst_2014} \\
SeparationsMatrix & A facility for elemental separations of used fuel & \cite{huff_streamblender_2014} \\
StreamBlender & A facility for fuel fabrication from reprocessed streams & \cite{huff_streamblender_2014} \\
\hline
\end{tabularx}
\caption{A diverse set of archetypes under development reflect the diverse
needs of researchers at various institutions. These archetypes, contributed
outside of the \Cyclus core and \Cycamore libraries are the first demonstration
of community-driven development in a fuel cycle simulator.}
\label{tab:archetypes}
\end{table}

\subsection{Simulations}
\label{ref:simulation}
%Inpro example (is this still running or did we deprecate it with 1.0?)
